### 2015-01-19 src/discussion.Rnw
update

To be added.

>>>>

We will analyze each of the different types of mutation reduction strategies in
detail, and summarize the broad patterns we see at the end.

\subsubsection{Operator Selection}
From Table~\ref{tbl:selective}, looking at the test and assert utility, we
see that there are a few selective strategies that seem to score a positive
test utility. Notably, the statement modification strategy sselective does
about 1.86\% better than the random selection for test utility, and has
similar advantage in assert utility. It also seem to have a slight advantage
of 0.27\% in the strategy effectivenss.

The statistical analysis in Table~\ref{tbl:ttests} also suggests a positive
mean and a $p-value < 0.01$ for this result.

For N-selection, which is given in Table~\ref{tbl:nselection}, The best
utility was on removal of \Pitnvmc, \Pitrv, \Pitic, \Pitdc, and \Pitnc which
resulted in a test utility advantage of 2.67\%. It also have the best positive
strategy effectiveness of 0.29\%. However, the difference was not significant
using t-tests in Table~\ref{tbl:ttests} $p-value > 0.01$.~\footnote{The
difference between Table~\ref{tbl:nselection} and Table~\ref{tbl:ttests}
is due to test or mutant number being zero for baseline, and hence remvoed
for computing percentage}.

Using single operators, we get a better result of 7.77\% for \Pitrv, which
is also significant at $p-value < 0.01$.

\subsubsection{Stratified sampling over operators}
For stratified sampling over operators in Table~\ref{tbl:opsample}, the best
result appears to be at $\frac{1}{8}$, which gives an advantage of 1.64\% over
baseline. However, we note that the strategy effectiveness is negative. For
t-test, since this is a continuum, we only inspected if the strategy as a
whole (not particular fractions) hold any advantage. The t-test suggests that
there is no significant difference from the baseline for this kind of sampling.

\subsubsection{Stratified sampling over program elements}
For stratified sampling over program elements in Table~\ref{tbl:element},
there appears a small consistent advantage for most sample fractions. The best
utility achieved was 3.85\% for class based $\frac{1}{16}$ sample. As before,
as this is a continuum, we only checked whether this kind of sampling has any
significant advantage as a whole with t-test. The t-test suggests that all
sampling over elements have a small but consistent advantage $p-value < 0.01$

A general pattern that we can glean from this analysis is that none of
the mutation reduction strategies appear to be practically better than
our baseline -- the simplest strategy of all -- the random selection
strategy. This suggests that at least from the perspective of a software
tester wishing to use mutation analysis as an evaluation criteria to judge
when or which tests to add, random sampling is the easiest way to reduce
the computational requirements of mutation analysis. This assumes even more
importance when we consider that the adequate random sample of mutants
increases at a rate less than $O(n^\frac{1}{4})$ when the program size
increases linearly~\cite{zhang2014empirical}.
